---
title: "FINAL PROJECT"
author: "Daniel Soria"
date: "9/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

```{r}
library(dplyr)
```

```{r}
Pums <- read.csv(file = "C:/Users/gsoria/Documents/Fall 2019/DA 6233 Malshe/Final Project/pums.csv", header = TRUE)
```

```{r}
head(Pums, 25)
```

```{r}
Owner1 <- filter(Pums, PCT1 == 100, EDUC1 %in% c(1,2,3,4,5,6,7))

head(Owner1, 30)
```


```{r}
Owner1 %>% 
  select(FOUNDED1, 
PURCHASED1, 
INHERITED1, 
RECEIVED1 ) %>% 
  mutate(FOUNDED1 = ifelse(FOUNDED1 == 2, 0, 1),
         PURCHASED1 = ifelse(PURCHASED1 == 2, 0, 1),
         INHERITED1 = ifelse(INHERITED1 == 2, 0, 1),
         RECEIVED1 = ifelse(RECEIVED1 == 2, 0, 1)) %>% 
  summarize_all(sum, na.rm = TRUE) %>%
  reshape2::melt() %>% 
  ggplot(aes(x = variable, y = value, fill = variable)) +
  geom_col() +
  geom_text(aes(label = scales::comma(value)), vjust = -0.3) +
   labs(x="Acquisition Method",
       y="Count",
       title="How Business was Acquired") +
  
  scale_x_discrete(breaks = c(1,2,3,4)) +
  
  scale_fill_discrete(name= "Acquisition Method", labels= c("Founded", "Purchased" , "Inherited", "Received")) +
  
  scale_y_continuous(labels = scales::comma_format())+

  theme_bw()




```




# Of the single owned business, what is the level of education
```{r}
ggplot(Owner1, aes(EDUC1, fill = factor(EDUC1))) + 
  
  geom_bar()+
  
   labs(x="Education Level",
       y="Count",
       title= "Education of Single Business Owners") +
  
scale_x_continuous(breaks = c(1,2,3,4,5,6,7)) +
  
  scale_y_continuous(labels = scales::comma_format())+
  
  scale_fill_discrete(name="Education Level", labels= c("Less Than High School", "High School" , "Technical School", "Some College", "Associate's", "Bachelor's", "Master's +")) +
  

  
 
  theme_bw()

```



# How did they acquire the business?
# I need to create a bar chart that has count on the Y axis and only counts the instances where a person selected 1 for founded, 1 for purchased, 1 for inherited, and 1 for received as gift.

#I know that the counts (y axis) should read 557k for founded, 11k for inherited, 93k for purchased, and 13k for received as gift, however I don't know 

#Should I create new subsets(seen below) and then put them all on the x - axis? Or is there a way to use the original data set and use a 'sumif' type function...

FOUNDED1 
PURCHASED1 
INHERITED1 
RECEIVED1 
ACQUIRENR1 
```{r}
FOUNDED1sub <- filter(Owner1, FOUNDED1 == 1, FOUNDED1 %in% c(1))

PURCHASED1sub <- filter(Owner1, PURCHASED1 == 1, PURCHASED1  %in% c(1))

INHERITED1sub <- filter(Owner1, INHERITED1 == 1, INHERITED1  %in% c(1))

RECEIVED1sub <- filter(Owner1, RECEIVED1 == 1, RECEIVED1  %in% c(1))

head(RECEIVED1sub, 30)
```

#convert 2s to 0
#use geom bar



```{r}
ggplot(Owner1,aes(FOUNDED1, fill = factor(FOUNDED1))) +
  
 geom_bar(position = "dodge", color = "black") +
 labs(title = "How Business was Acquired",
      x = "Method",
      y = "Count") +
    
 scale_fill_discrete(name = "Answered",
                     labels = c("Answered 1","Answered 2", "Answered 3", "Answered 4")) +
  
 scale_x_continuous(breaks = c(1:4),
                    labels = c("Founded","Purchased", "Inerited", "Gift")) +
  
 theme(axis.text.x = element_text(angle=30))+
 scale_y_continuous(labels = scales::comma_format()) +
 theme(axis.text.x = element_text(angle=30)) +
 theme_classic()
```


```{r}
ggplot(data = Owner1, aes(FOUNDED1sub))
```



```{r}
ggplot(FOUNDED1sub, aes(FOUNDED1, fill = FOUNDED1)) + 
  
  geom_histogram()+
 
  theme_bw()
```

```{r}
Acquired <- Owner1(value=)
```


```{r}
ggplot(Owner1, aes(EDUC1, fill = EDUC1)) + 
  
  geom_bar(show.legend = TRUE)+
  
  labs(x="Education Level",
       y="Count",
       title="Education of Single Business Owners") +
  
  #Need legend 
 
  theme_bw()
```


# How much money did they start the business with?
```{r}
ggplot(data = Owner1, mapping = aes(x = #NEED MONEY VALUE)) +
  
  geom_histogram() +
  
  theme_bw()
```

#BORN IN THE US? BORN1